redraft backup

### 2020-04-02 draft_exploration.Rmd
made redraft into a function and created backup rmd for the function

@@

# filtering the unsigned high school data for only draft picks after 1990

hs_unsigned_trimyear <- hs_unsigned %>%
  filter(year >= 1990)

@@

count_unsigned_hs <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & year <= 2015) %>%
  count() %>%
  pull(n)

@@

trimyear_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & year <= 2015) %>%
  select(player_id)

@@

unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & draft_round <= 20 & year <= 2015) %>%
  select(player_id)

@@

```
Findings from above: 50.8 percent of players that turned down the draft out of
high school from 1990-2015 were drafted again. 73.3 percent of players that turned down a top 20
round draft pick out of high school from 1990-2015 were drafted again. The average initial round
of top 20 high school picks to turn down the draft was 12.99. When they are
redrafted, the average pick is round 16.38, a fair drop.

@@

@@

>>>>

Findings from master redraft function (can be found in redraft_backup.Rmd) :
50.8 percent of players that turned down the draft out of high school from
1990-2015 were drafted again. 73.3 percent of players that turned down a top 20
round draft pick out of high school from 1990-2015 were drafted again. The
average initial round of top 20 high school picks to turn down the draft was
12.99. When they are redrafted, the average pick is round 16.38, a fair drop.

@@

redraft_master <- function(startyear, endyear = startyear + 4) {
# filtering the unsigned high school data for only draft picks after 1990

hs_unsigned_trimyear <- hs_unsigned %>%
  filter(year >= startyear)

@@

count_unsigned_hs <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & year <= endyear) %>%
  count() %>%
  pull(n)

@@

trimyear_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & year <= endyear) %>%
  select(player_id)

@@

unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & draft_round <= 20 & year <= endyear) %>%
  select(player_id)

@@

percent_redrafted_20
}

@@

full_redraft_percent <- function(startyear, endyear = startyear + 4) {

hs_unsigned_trimyear <- hs_unsigned %>%
  filter(year >= startyear)

count_unsigned_hs <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & year <= endyear) %>%
  count() %>%
  pull(n)

trimyear_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & year <= endyear) %>%
  select(player_id)

percent_redrafted_hs

}

full_redraft_percent(1990, 2015)

@@

```{r}
round_redraft_percent <- function(startyear, endyear = startyear + 4, rounds = 20) {

hs_unsigned_trimyear <- hs_unsigned %>%
  filter(year >= startyear)

unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & draft_round <= rounds & year <= endyear) %>%
  select(player_id)

percent_redrafted_20

}

round_redraft_percent(1990, 2015, 20)

```{r}
prior_mean_round <- function(startyear, endyear = startyear + 4, rounds = 20) {

hs_unsigned_trimyear <- hs_unsigned %>%
  filter(year >= startyear)

unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & draft_round <= rounds & year <= endyear) %>%
  select(player_id)

avg_round_20_hs

}

prior_mean_round(1990, 2015, 20)
```

```{r}
post_mean_round <- function(startyear, endyear = startyear + 4, rounds = 20) {

hs_unsigned_trimyear <- hs_unsigned %>%
  filter(year >= startyear)

unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & draft_round <= rounds & year <= endyear) %>%
  select(player_id)

avg_round_redrafted_20

}

post_mean_round(1990, 2015, 20)

### 2020-04-02 redraft_backup.Rmd
made redraft into a function and created backup rmd for the function

---
title: "Draft Exploration"
author: "Chase Bookin"
date: "March 21, 2020"
output: html_document
---

@@

```{r, echo=FALSE}
draft_2000_2012 <- draft %>%
  filter(year >= 2000 & year <= 2012)

draft_2000_2012 <- draft_2000_2012 %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
  mutate(ignore = 1) %>%
  group_by(draft_round) %>%
  summarize(percent_mlb = sum(mlb_made) / sum(ignore))

ggplot(draft_2000_2012, mapping = aes(draft_round, percent_mlb)) +
  geom_col() +
  theme_economist_white() +
  labs(
    x = "Draft Round",
    y = "Percent to reach Major Leagues",
    title = "Percent of Draft Picks by Round to Reach the Majors",
    subtitle = "Data from 2000-2012 drafts"
  ) 
```

```{r, echo=FALSE}
grow_talent <- master %>%
  filter(source == "H" & signed == "Y") %>%
  mutate(decade = ifelse(year %in% 1970:1979, 1970,
                                 ifelse(year %in% 1980:1989, 1980,
                                        ifelse(year %in% 1990:1999, 1990,
                                               ifelse(year %in% 2000:2009, 2000,
                                                      ifelse(year %in% 2010:2019, 2010, NA)))))) %>%
  filter(year >= 1980 & year <= 2009) %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
  mutate(ignore = 1) %>%
  group_by(teamname) %>%
  summarize(percent_mlb = sum(mlb_made) / sum(ignore))

ggplot(grow_talent, mapping = aes(x = reorder(teamname, -percent_mlb), percent_mlb)) +
  geom_col() +
  theme_economist_white() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    x = "Team",
    y = "Percent of High School Picks to MLB",
    title = "Percent of High School Picks to MLB by Team",
    subtitle = "Data: 1980-2009 Drafts"
  )

```{r, echo=FALSE}

hs_signed <- master %>%
  filter(source == "H" & signed == "Y") %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0))

hs_signed_90_09 <- hs_signed %>%
  mutate(ignore = 1) %>%
  group_by(draft_round) %>%
  filter(year >= 1990 & year <= 2009) %>%
  filter(draft_round <= 40) %>%
  summarize(percent_mlb = sum(mlb_made) / sum(ignore))

ggplot(hs_signed_90_09, mapping = aes(draft_round, percent_mlb)) +
  geom_col() +
  theme_economist_white() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    x = "Round",
    y = "Percent of Signed High School Picks to MLB",
    title = "Percent of Signed High School Picks to MLB by Round",
    subtitle = "Data: 1980-2009 Drafts"
  )

@@

Findings from master redraft function (can be found in redraft_backup.Rmd) :
50.8 percent of players that turned down the draft out of high school from
1990-2015 were drafted again. 73.3 percent of players that turned down a top 20
round draft pick out of high school from 1990-2015 were drafted again. The
average initial round of top 20 high school picks to turn down the draft was
12.99. When they are redrafted, the average pick is round 16.38, a fair drop.

@@

redraft_master <- function(startyear, endyear = startyear + 4) {
# filtering the unsigned high school data for only draft picks after 1990

hs_unsigned_trimyear <- hs_unsigned %>%
  filter(year >= startyear)

@@

count_unsigned_hs <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & year <= endyear) %>%
  count() %>%
  pull(n)

@@

trimyear_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & year <= endyear) %>%
  select(player_id)

@@

unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & draft_round <= 20 & year <= endyear) %>%
  select(player_id)

@@

percent_redrafted_20
}

full_redraft_percent <- function(startyear, endyear = startyear + 4) {

hs_unsigned_trimyear <- hs_unsigned %>%
  filter(year >= startyear)

count_unsigned_hs <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & year <= endyear) %>%
  count() %>%
  pull(n)

trimyear_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & year <= endyear) %>%
  select(player_id)

percent_redrafted_hs

}

full_redraft_percent(1990, 2015)

```{r}
round_redraft_percent <- function(startyear, endyear = startyear + 4, rounds = 20) {

hs_unsigned_trimyear <- hs_unsigned %>%
  filter(year >= startyear)

unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & draft_round <= rounds & year <= endyear) %>%
  select(player_id)

percent_redrafted_20

}

round_redraft_percent(1990, 2015, 20)

```{r}
prior_mean_round <- function(startyear, endyear = startyear + 4, rounds = 20) {

hs_unsigned_trimyear <- hs_unsigned %>%
  filter(year >= startyear)

unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & draft_round <= rounds & year <= endyear) %>%
  select(player_id)

avg_round_20_hs

}

prior_mean_round(1990, 2015, 20)
```

```{r}
post_mean_round <- function(startyear, endyear = startyear + 4, rounds = 20) {

hs_unsigned_trimyear <- hs_unsigned %>%
  filter(year >= startyear)

unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & draft_round <= rounds & year <= endyear) %>%
  select(player_id)

avg_round_redrafted_20

}

post_mean_round(1990, 2015, 20)

>>>>

---
title: "redraft backup"
author: "Chase Bookin"
date: "April 2, 2020"
output: html_document
---

@@

@@

@@

# filtering the unsigned high school data for only draft picks after 1990

hs_unsigned_trimyear <- hs_unsigned %>%
  filter(year >= 1990)

@@

count_unsigned_hs <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & year <= 2015) %>%
  count() %>%
  pull(n)

@@

trimyear_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & year <= 2015) %>%
  select(player_id)

@@

unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
  filter(draft_numb == 1 & draft_round <= 20 & year <= 2015) %>%
  select(player_id)

@@

```
Findings from master redraft function (can be found in redraft_backup.Rmd) :
50.8 percent of players that turned down the draft out of high school from
1990-2015 were drafted again. 73.3 percent of players that turned down a top 20
round draft pick out of high school from 1990-2015 were drafted again. The
average initial round of top 20 high school picks to turn down the draft was
12.99. When they are redrafted, the average pick is round 16.38, a fair drop.
